\documentclass[../../../main.tex]{subfiles}
\begin{document}

\subsection{Academic contributions}

\begin{itemize}
    \item \textbf{Publication in peer-reviewed journal}: Bernadi-Forteza, A.; Mallon, M.; Velasco-Gallego, C.; Cubo-Mateo, N. A Systematic Review on the Generation of Organic Structures through Additive Manufacturing Techniques. Polymers 2024, 16, 2027. https://doi.org/10.3390/polym16142027 \cite{alex}.
    \item \textbf{Paper under work to submit to peer-reviewed journal:} Bernadi-Forteza, A.; Mallon, M.; Makaya, A.; Cubo-Mateo, N. A Novel Method for Generating Self-Supporting Stochastic Porous Structures for Bone Tissue Engineering. 
    \item \textbf{Oral Exposition at I Jornadas de Jóvenes Investigadores (Oral presentation awarded as the second best oral presentation):} Diseños avanzados de estructuras no regulares para la fabricación de andamios óseos sin soporte. Bernadí-Forteza, A. Universidad de Nebrija, Spain. November 2024.
    \item \textbf{Oral Exposition at XLVI International Congress of the Iberian Society of Biomechanics and Biomaterials (SIBB'24):} Advanced non-regular lattice designs for supportless bone scaffold manufacturing
Alex Bernadí-Forteza , Juan José Uriarte , Nieves Cubo-Mateo. Valencia, Spain. December 2024.
    \item \textbf{Poster at European Society of Biomaterials - P324:} Advanced non-regular lattice designs for supportless bone scaffold manufacturing
Alex Bernadi-Forteza, Michael Mallon, Nieves Cubo-Mateo, Torino, Italy. September 2025.
    \item \textbf{Oral Exposition at II Jornadas de Jóvenes Investigadores:} Diseños avanzados de estructuras no regulares para la fabricación de andamios óseos sin soporte. Bernadí-Forteza, A. Universidad de Nebrija, Spain. November 2025.
    
\end{itemize}

\subsection{Technological contributions}

During the development of this thesis, three code repositories written in Python were developed and published on the author's Github portal\footnote{Author's Github page: \href{https://github.com/panallax}{https://github.com/panallax}}. The repositories are listed below, along with a brief description at the time of publication of this work. Please note that the names of the repositories may be subject to change, but they will always be available on the author's portal.

\begin{itemize}
    \item \textbf{Mesh-gen:} Repository for generating self-supporting graph-like stochastic structures. Link: \href{https://github.com/panallax/mesh-gen}{github.com/panallax/mesh-gen}.
    \item \textbf{Spyffness:} A Python library for structural analysis. Link: \href{https://github.com/panallax/Spyffness}{github.com/panallax/Spyffness}.
    \item \textbf{digitRecorder:} A Python package for  OCR 7-segment digit images. \\ Link: \href{https://github.com/panallax/digitRecorder}{github.com/panallax/digitRecorder}.
\end{itemize}


\end{document}